\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-09 paper/ResponseToReviewers.tex

\myexternaldocument{main}

\begin{document}
\hfill \today
%\section{}
%\subsection{}

\noindent \textbf{Prof. Chris Jarrold}\\
\noindent \textbf{Associate Editor}\\
\noindent \textbf{Journal of Memory and Language}
\vskip 1em

\noindent \textbf{Response letter for Submission JML-24-17}
\vskip 2em
\noindent Dear Prof. Jarrold, 
\vskip 1em
Together with my co-authors Shravan Vasishth and Himanshu Yadav, who was added during the revision, I would like to submit our revision of the article titled ``Do syntactic and semantic similarity lead to interference effects? Evidence from self-paced reading and event-related potentials using German''.
We are grateful for thoughtful and constructive comments and suggestions from yourself and the reviewers, and feel that the quality of the manuscript has been greatly improved by the revisions.

@@

You noted in your decision letter that the manuscript could potentially be a valuable contribution to the special issue, a view largely shared by the reviewers.

Reviewer 1 was concerned with some decisions that we had made in our computational modeling and statistical analyses and the interpretation of the results. In response to the concerns about our statistical analyses, we have completely re-done the analyses of the reading times and ERP data and added analyses of the previous data. We brought Himanshu Yadav into the project to refine our modeling, including the addition of a third model, and carry out model comparisons. We believe that these new analyses strengthen our initial interpretation that our study shows semantic interference, but no syntactic interference and no interaction.

Reviewer 2 primarily raised concerns regarding our experimental design. In response to these concerns, we have emphasized that we used a well-established design that was previously published in, among other journals, the \textcolor{red}{\textit{Journal of Memory and Language}}. We now stress in the paper that we are building on previously published work by directly comparing the statistical inferences, using Bayes factors, from the present and previous studies that use exactly the same design.

@@

You will see that all three of the reviews are thorough, well-informed, and detailed and I am grateful to the reviewers for the care and time they have clearly put in to reading the manuscript. My own reading aligned with Reviewer 1's assessment in that I found your paper to be very clearly written and enjoyable to read. Your very good sample sizes and sophisticated analyses and modelling suggest to me that this work has the potential to make a strong contribution to our special issue.

However, I am far from being an expert in this area, and the (therefore much more knowledgeable) reviewers have raised a number of issues with the paper, some of which I judge to be substantive. For this reason I have come to a 'revise and resubmit' decision. If you do revise and resubmit your paper, as I hope you will, I will approach the same set of reviewers to see if they are able to re-review (and obviously there is no guarantee of acceptance at that stage).

In revising your paper you should take into account all of the reviewer's points. However, there are two themes that I picked out as particularly important.

First, \textbf{Reviewer 2 raises a potentially serious concern that your particular manipulation of syntactic dis/similarity might not be expected to lead to substantial syntactic interference (their point 1)}. In other words, the questions are whether one would ever expect to see much of this effect with your design and whether a more appropriate design would lead to stronger findings. Some of Reviewer 3's points (see their paragraph starting `The authors attribute ...' and their final summary comment) are perhaps in the same vein.''
\end{quote}

\subsection*{Response to E.1}
We have used a well-studied design that was previously published in the \textcolor{red}{Journal of Memory and Language}, among other places. The previously published studies use exactly the same design, specifically the same syntactic retrieval cue, and found effects of syntactic interference \citep{vandyke07,mertzen}.
It is possible that the reviewer is right to not expect the design to lead to decisive syntactic interference effects because the syntactic manipulation might not be appropriate. However, we are building on the previously published claim that this design leads to syntactic interference. We believe that our results are a valuable contribution to the literature on syntactic interference, and serve as an important counterpoint to the previously published claims \citep{vandyke07, mertzen}. We added the following text to our General Discussion on page \pageref{only_this_design} to emphasize that our findings and conclusions only apply to the present design:

\begin{quote}
    \Paste{only_this_design}
\end{quote}

The reviewer's objection can and should be pursued in a future study that uses a design that the reviewer would consider appropriate, but this would require a completely new paper with a different research focus (namely, what is an appropriate syntactic manipulation that would lead to interference?). We now mention in the General Discussion on page \pageref{future_work}
that such a future investigation is needed:

\begin{quote}
    \Paste{future_work}
\end{quote}

@@

\subsection*{Comment E.2}

\begin{quote}
``Second, a couple of Reviewer 1's comments (e.g., their point 2, and their final point about priors) relate to the fact that \textbf{there actually is some evidence for a degree of syntactic interference in aspects of the data, particularly perhaps in terms of the interaction and the combination with high semantic similarity, that you risk underplaying} (see also Reviewer 2's point 5).''
\end{quote}

\subsection*{Response to E.2}
We have re-done our analyses in response to the concerns raised by the reviewers and the Bayes factors from the revised analyses still do not provide evidence for syntactic interference or the interaction. As an overview of the revised Bayes factor analyses, we show Figures \ref{fig:spr_bfs} and \ref{fig:eeg_bfs} below. Figure \ref{fig:spr_bfs} shows the Bayes factor analysis of the self-paced reading data. There was evidence against syntactic interference under all priors in the pre-critical and critical region. Only in the spill-over region, there was anecdotal evidence (BF$_{10}$ = 2.8) for a small syntactic interference effect ($\pm$ 8 ms). Similarly, there was evidence against the interaction under all priors in the pre-critical and spill-over regions. Only in the critical region, there was anecdotal evidence (BF$_{10}$ = 1.4) for a small interaction effect ($\pm$ 8 ms).

@@

Taken these Bayes factor results together (at best anecdotal evidence for small effects in the size of an 8\,ms reading time difference or an 0.2\,$\mu V$ difference in brain responses), we are confident that in our data, there was no evidence for an effect of considerable size of neither syntactic interference nor the interaction.

\setcounter{figure}{10}
\Paste{fig_bf_eeg}

\subsection*{Comment E.3}
\begin{quote}
``Finally, I would also add that while I agree with Reviewer 1's assessment that your paper would fit well in the special issue, \textbf{as someone more versed in the memory than the language literature I thought you could be more explicit about how your findings do integrate both of these two areas.}''
\end{quote}

\subsection*{Response to E.3}
Our work is situated in the cue-based retrieval framework which has been built over the last decades \citep{Lewis2005, mcelree}. Its main assumption is that sentence processing relies on skilled memory processes, with a focus on memory retrieval. We built on this assumption and focus on the question which specific retrieval cues are being used during subject-verb dependency resolution. Our findings showed that the retrieval cues generated at the verb are highly specific (including hierarchical syntactic information) and can successfully identify the subject as the retrieval target. Therefore, the present findings further support the assumption that sentence processing relies on skilled memory retrieval. We have emphasized the theoretical grounding of our work by adding more references to the introduction on page \pageref{intro}:

\begin{quote}
    \Paste{intro}
\end{quote}

Additionally, we have added the following text to the General Discussion on page \textcolor{red}{X} to emphasize the theoretical grounding of our work:

@@

\subsubsection*{Response to R1.2}
We have re-done the Figure to reflect our revised modeling. We hope that the scale of the new Figure \ref{fig:model_predictions_ERP} is easier to read (see below in our Response to R1.3).

\subsection*{Comment R1.3}
\begin{quote}
``In my reading, the discrepancy mainly comes from the fact that the decision to neglect syntactic interference is based on Bayes factors (see also below), but when matching the model predictions to actual results (p. 39-42), the match is done on posterior distributions, which do show a positive effect of interaction (the self-paced reading study) and an effect of syntactic interference (the self-paced reading study and the EEG study). \textbf{I think what the authors could do to at least partially address this issue is to be more explicit about model comparisons. They could leverage their use of Bayes factors to compare different computational models - the one proposed in this paper, which hard-codes that only the syntactic target is selected, the one based on Mertzen et al., possibly with varying priors, and, possibly, a null model which does not predict any interference (e.g., it hard-codes that only the target is retrieved).}''\end{quote}

\subsubsection*{Response to R1.3}
As suggested, we have implemented a null model (no interference), leaving us with a total of three computational models (the null model, the three-cues model by \textcite{mertzen} and our newly proposed two-cues model). We use Bayes factors to quantitatively compare these models. The result of this model comparison is that the two-cues and three-cues models outperform the null model. Additionally, our new two-cues model performs slightly better than the three-cues model by \textcite{mertzen}. We have described the new modeling and model comparisons starting page \pageref{modeling}:

\begin{quote}
    \Paste{modeling}
\end{quote}
\newpage

@@

\subsection*{Comment R1.4}
\begin{quote}
``3. Comparison to previous findings: Syntactic interference has been observed previously. The authors discuss in detail Van Dyke (2007) and Mertzen et al. (2023) as two studies that argue for syntactic interference. This is in contrast to the current study, which is claimed not to show syntactic interference. One problem for me is that we are not making a fair comparison: the current study bases its interpretation on Bayes factors, which were not used in Van Dyke or Mertzen et al. To be sure, my point is not that Bayes factors should not be used (of course, I find it good that they are used to compare hypotheses), just that the comparison between this study and the other findings is far from straightforward. If we only check posterior distributions, which were explored in Mertzen et al. for their conclusions, we do see some effect of syntactic interference - e.g., the predominantly negative credible interval in the EEG study. As far as I can see, \textbf{to really make a sensible comparison, one would either have to reanalyze Mertzen and Van Dyke's data using Bayes factors or be more precise in explaining how the posterior distributions in this study differ from previous studies} - just looking at the posteriors, they do not seem to paint such different pictures between the current study and Mertzen et al. ''\end{quote}

\subsubsection*{Response to R1.4}
In the revised manuscript, we are now more explicit about the comparison to previous findings. We have added a new figure (Figure \ref{fig:previous_vs_present}) to the General Discussion. The new figure shows the estimates of the previous studies and Bayes factors which we have computed for the previous studies, along with our own estimates and Bayes factors. The Bayes factors of the present and previous studies align well with one exception: The previous studies found evidence for syntactic interference in the pre-critical
region, while our study did not. The following description of the estimates and Bayes factors of the present and previous studies and their interpretation was added to the manuscript, starting page \pageref{comparison}:
\setcounter{figure}{12}

\begin{quote}
    \Paste{comparison}
\end{quote}

@@

\newpage

\subsection*{Comment R1.5}
\begin{quote}
``Another problem I have is more general and has to do with progress in science. The authors in my reading find the current findings more convincing than, say, Mertzen et al. study. I get that the current study is convincing (I do find it convincing) but that does not disqualify what Mertzen et al. found in any way - both results co-exist. Ideally, I would expect that a model would be able to explain the current data, but also the past data. I get it that this is not always possible but then, \textbf{it would be good if the authors make their position explicit - either by admitting that only some data can be captured, or, if the authors believe that the past data should be ignored, it should be explained why this is so.}

All in all, I think the interpretation of the data and the model have to be strengthened to meet requirements 1-3. Alternatively, the manuscript should explicitly admit issues in the proposed interpretation - that is, explain that the model fails to capture encoding interference (point 1 if I am right), explain why the model underpredicts interference in syntax/interaction and explain why it is enough, at least for now, to only model the current findings and to put previous findings aside (assuming they actually differ - see point 3 about Bayes factors above).''\end{quote}

\subsubsection*{Response to R1.5}
About why our results diverge from previous studies' and whether we think our results are correct and the previous work is not, we have no position on this. We are simply reporting what we found. Contradictory results have been reported for many phenomena: e.g., reflexives processing \citep{jaeger_etal_2020}, main verb/reduced relative garden paths (\textcolor{red}{REF?}), predictive parsing effects \citep{nieuwland_etal_2018}, local coherence \citep{lcpaape2023}. The only way to resolve contradictions in the literature is by carrying out adequately powered studies in the future that can distinguish between the theoretical claims. Our work does not stand out as an anomaly; if anything, it's quite the opposite. We have added a discussion of divergent results in the literature to page \pageref{not_an_anomaly} in the General Discussion:

\begin{quote}
    \Paste{not_an_anomaly}
\end{quote}

@@

\subsection*{Comment R1.6}
\begin{quote}
``Semantic encoding interference vs.\ acceptability\\
===========================

It is proposed that the semantic interference in the self-paced reading study is due to encoding. This interpretation is supported by the fact that we observe increased reading times from the moment that the +animate distractor is read (nicely shown in Figure 3). I wonder whether an even more straightforward interpretation is possible here. Could the effect of increased reading times simply be due to the fact that the +animate distractor is not as good as the -animate distractor in this context? That is, the effect has nothing to do with encoding interference, it's just a consequence of the fact that, e.g., in (2a) the statement that "the burglar was awful" is harder to make sense of than that "the loss was awful". \textbf{I think one easy way to check it would be to run an acceptability/plausibility study which checks whether the +animate version and the -animate version are comparable in their acceptability.} I know that the manuscript mentions a possible confound due to plausibility (p. 22, 23) but as far as I could understand it is assumed that this confound would only affect the syntactic manipulation, not the semantic one. However, I think the semantic manipulation could just as well result in more or less plausible sentences.''\end{quote}

\subsubsection*{Response to R1.6}
We ran the suggested plausibility judgement experiment. The -animate distractor is indeed slightly more plausible in the context than the +animate distractor. To investigate whether this plausibility difference is driving the semantic interference effect in our SPR data, we ran a Bayesian hierarchical mixed model on the reading times of the pre-critical region which included plausibility as a co-predictor and find that there is still evidence for an independent semantic interference effect. We discuss the plausibility confound and the additional analyses in the revised manuscript starting on page \pageref{plausib_anim_inan}:

\begin{quote}
    \Paste{plausib_anim_inan}
\end{quote}

@@

\newpage

\subsection*{Comment R1.7}
\begin{quote}
``Intercept-only models\\
=============

Models with intercept-only random-effect structures are used for the data analysis. I see why this has to be done for Bayes factors. I wonder, though, whether this justifies the use of intercept-only models to find posterior distributions of parameters. I would worry that given that all Bayes models have intercept-only random-effect structures, we probably overestimate the size of fixed effects (e.g., in Figure 4). \textbf{Why not doing the following: one could use models with full random effect structure for estimation of posterior distribution of parameters, and then switch to intercept-only models to calculate Bayes factors,} since more complex models lead to unstable Bayes factors.''\end{quote}

\subsubsection*{Response to R1.7}
We have recomputed all our Bayes factors using the Savage-Dickey method. With this method, we were able to compute Bayes factors for models with complex random effect structures. We have re-run all models with full random effect structures and updated all results in the manuscript accordingly. The results did not change qualitatively.

@@

Various priors are considered for Bayes factors. \textbf{Of course, it is good to explore several values but I wonder whether it is justified to conclude that syntactic interference or interaction should be excluded if they are not supported in models with unreasonably large priors (e.g., N+(0, 0.1)). Would anybody expect that interference is in range of 0.1 log-ms? As one of the authors of this manuscript nicely showed in Jager et al. (2017) and Schad et al. (2022), interference effects are small (at least for subject-verb agreement and ungrammatical illusions). Given that, I don't understand why we require a BF in favor of interference for a prior that is of size N+(0, 0.1). Shouldn't a smaller prior distribution suffice as evidence? This brings me again to my confusion in what the experiments actually show. The authors seem to argue that the only interference is the semantic one and they base the conclusion on large priors. But focusing on small priors (N+(0, 0.05) for spr, N-(0, 0.5) for EEG)), one could conclude that the interaction/syntactic interference might be present after all. Is there an independent reason to select the former priors over the latter for one's interpretation? To be sure, I don't want the authors to change the interpretation, but I would like to see either a more explicit argumentation why we should base our conclusion on such and such priors, or a more reflection in the text that explicitly states that the results are not equivocal and the current study is still compatible with a position that syntactic interference and/or interaction are real.}''\end{quote}

\subsubsection*{Response to R1.8}
BFs do not to need to be strongly in favor of an effect across all investigated priors to conclude that an effect is supported. However, to draw decisive conclusions in favor of an effect, the evidence for that effect should be stronger than anecdotal for at least a subset of reasonable priors.

The meta-analysis of reading time studies by \textcite{jaeger_etal_2017} showed that the pooled estimate of inhibitory interference across studies with similar designs as ours was indeed small (13.1 ms, page 327), but some studies showed effects around 50 ms (e.g., two of the sub-experiments from \cite{vandyke07}) and one experiment by Franck et al., (2015) even showed an estimate above 100 ms (see Figure 2 on page 329 of \cite{jaeger_etal_2017}). Because such large interference effects have been found previously (see also our new Figure \ref{fig:previous_vs_present} showing all estimates of \cite{vandyke07} and \cite{mertzen}), we believe that it is reasonable to explore a wide range of a priori effect sizes, specifically from $\pm$8 to $\pm$80 ms for the reading times.

@@

\noindent We added the following summary of the results to the Discussion on page \pageref{ERP_discussion}:

\begin{quote}
    \Paste{ERP_discussion}
\end{quote}

\subsection*{Comment R2.6}
\begin{quote}
``7. \textbf{It is noteworthy that the general discussion does not mention or discuss the works showing that hierarchical intervention matters in agreement attraction and that pre-date all the studies mentioned in the several parentheticals. I have in mind Franck et al. 2002, 2006 and 2011, for instance. These works offer a treatment of attraction in terms of intervention and, as far as my knowledge goes, these are the first studies highlighting the crucial role of hierarchical interference effects. While authors mention other papers about agreement attraction, they seem to overlook these particular ones.}''
\end{quote}

We agree that this line of work is highly relevant for our paper. We have added the suggested references (and some more by the same and other authors) to the introduction (page \pageref{franck_refs}) and General Discussion (page \pageref{future_work}):

\begin{quote}
    \Paste{franck_refs}
\end{quote}

\begin{quote}
    \Paste{future_work}
\end{quote}

### 2024-08-11 paper/main.tex
Updated via the Open Science Framework

\Copy{modeling}{\textcolor{blue}{The \citet{Lewis2005} model is generally used to predict reading times. Recently, \textcite{mertzen} presented simulations for the present design that predicted approximately equally sized effects of syntactic and semantic interference in the reading times of the critical verb. We found that the reading times at the critical verb were confounded by pre-critical effects, which were best explained by \textit{encoding} interference. Therefore, it makes no sense to compare the results from the present SPR experiment to predictions from the Lewis and Vasishth (2005) model of sentence processing as skilled memory \textit{retrieval}. Instead we use the Lewis and Vasishth (2005) model to generate predictions on the microvolt scale for ERP data. For this we adjust the scaling factor $F$ which usually links the activation of items in memory to retrieval times \citep{Lewis2005,anderson_etal_2004_ACT_R} to link memory activation to brain responses.} The modeling reported here is, to the best of our knowledge, the first time that the \citet{Lewis2005} model has been fit quantitatively to ERP data. We sampled the free scaling parameter $F$ from a uniform prior distribution ($Uniform(0.005, 0.04)$). This prior reflects the a priori belief that effects will range from 0.5 to 4 $\mu V$ with equal likelihood for all effect sizes in this range. This uninformative prior was chosen because there exists no previously published ERP data on the Van Dyke (2007) design. After sampling the scaling parameter, simulated data was generated from the model while holding all other parameters in the model at fixed values. \textcolor{blue}{We decided to model N400 amplitude differences because Bayes factors provided stronger evidence for the semantic interference effect on the N400 than on the P600 in the present ERP study. To reflect that larger predicted effect sizes correspond to more negative N400 amplitudes, the predicted effects from the model} were multiplied with $-1$. To avoid overfitting we fitted $F$ only to the semantic interference effect in order to generate posterior predictive distributions of the syntactic and semantic interference effects \textcolor{blue}{and their interaction.}

@@

\textcolor{blue}{Out of 100,000 iterations of ABC algorithm, we obtained only 6467 samples of $F$ for the 3-cues model, 1010 for the 2-cues model and 869 for the 1-cue model. This is not surprising given
the relatively wide prior on $F$. In future work, the posterior distribution, with range [-0.5, -0.1]\,$\mu V$, could be used as a basis for redefining a tighter prior on the scaling parameter $F$. Figure \ref{fig:model_predictions_ERP} shows the  posterior predictive distributions
of the effects of interest in comparison to the prior predictive distribution and our ERP
data. The prior and posterior predictions from the model with three cues show equally large effects of syntactic and semantic interference and an interaction. In contrast, the model using two cues, including a syntactic cue that utilizes syntactic hierarchy, predicts no effect of syntactic interference and no interaction, but a semantic interference effect. The model using one cue predicts no interference effects. The prior and posterior predictions of all models overlap with the effects of interest in the data. To evaluate the predictive fit of the three models to our data quantitatively, we used the likelihood-free k-fold cross-validation model comparison approach developed by \textcite{Yadavetal2022}.}

@@

\textcolor{blue}{For this k-fold cross-validation model comparison, we repeatedly computed how well each of the three models performed on a held-out small subset of the data after being trained on the remaining large subset of the data. We repeatedly left out 1/10$^{th}$ of the data which was then used as the test data, while the other 9/10$^{th}$ functioned as the training data. It was made sure that each of the 10 subsets included data from all participants, all items and all conditions. The models were trained by generating posterior predictive distributions by fitting the $F$ parameter to the posterior distribution of the effects of interest in the training data. Then these posterior distributions of $F$ were used to compute the likelihood of generating the held-out test data. The log of this likelihood is the predictive accuracy of the model. This was done 10 times. Then, we computed the sum and standard error of sum of the predictive accuracies of the models of each of the training and test datasets to gain the overall predictive accuracy, the expected log predictive density $\widehat{elpd}$, of each model. To evaluate the performances of the models, we compare the difference in the $\widehat{elpd}$ values between each model and the other two models (see Figure \ref{fig:elpd}). }

\begin{figure}
    \centering
    \caption{Comparison of the predictive accuracies of the three versions of the Lewis and Vasishth (2005) cue-based retrieval model on our ERP data. Each facet shows how the model in the facet's title performs in comparison to the models on the x-axis (positive $\widehat{elpd}$ differences correspond to better performance). Error bars show two times the standard error of the difference in $\widehat{elpd}$ values.}
    \label{fig:elpd}
    \includegraphics[width=\linewidth]{images/ELPD_difference.jpg}
\end{figure}

\textcolor{red}{add description of figure and conclusion of the modeling section}

%Thus, the theoretical assumption that is consistent with the observed ERP data is that although the parser uses the animacy cue exactly as proposed in previous work on cue-based retrieval, the syntactic cue keeps track of the clausal location of the subject. This is of course a speculative claim that would need to be further investigated empirically.

}\label{modeling}%end copy

>>>>

\label{modeling}\Copy{modeling}{\textcolor{blue}{The \citet{Lewis2005} model is generally used to predict reading times. Recently, \textcite{mertzen} presented simulations for the present design that predicted approximately equally sized effects of syntactic and semantic interference in the reading times of the critical verb. We found that the reading times at the critical verb were confounded by pre-critical effects, which were best explained by \textit{encoding} interference. Therefore, it makes no sense to compare the results from the present SPR experiment to predictions from the Lewis and Vasishth (2005) model of sentence processing as skilled memory \textit{retrieval}. Instead we use the Lewis and Vasishth (2005) model to generate predictions on the microvolt scale for ERP data. For this we adjust the scaling factor $F$ which usually links the activation of items in memory to retrieval times \citep{Lewis2005,anderson_etal_2004_ACT_R} to link memory activation to brain responses.} The modeling reported here is, to the best of our knowledge, the first time that the \citet{Lewis2005} model has been fit quantitatively to ERP data. We sampled the free scaling parameter $F$ from a \textcolor{blue}{truncated normal prior distribution ($Normal(0, 0.025)$) with a lower bound of 0 and an upper bound of 0.05. This prior reflects the a priori belief that effects will range from 0 to 5 $\mu V$ with higher likelihood for effect sizes below 1 $\mu V$ (see Figure \ref{fig:model_predictions_ERP}). This relatively uninformative prior was chosen because although there exists no previously published ERP data on the Van Dyke (2007) design it reflects the reasonable range of effect sizes in psycholinguistic ERP research.} After sampling the scaling parameter, simulated data was generated from the model while holding all other parameters in the model at fixed values. \textcolor{blue}{We decided to model N400 amplitude differences because Bayes factors provided stronger evidence for the semantic interference effect on the N400 than on the P600 in the present ERP study. To reflect that larger predicted effect sizes correspond to more negative N400 amplitudes, the predicted effects from the model} were multiplied with $-1$.

@@

\textcolor{blue}{Out of 200,000 iterations of ABC algorithm, we obtained only 40,748 samples of $F$ for the 3-cues model, 28,718 for the 2-cues model and 6,615 for the 1-cue model. This is not surprising given
the relatively wide prior on $F$. In future work, the posterior distribution, with range [-0.5, -0.1]\,$\mu V$, could be used as a basis for redefining a tighter prior on the scaling parameter $F$. Figure \ref{fig:model_predictions_ERP} shows the  posterior predictive distributions
of the effects of interest in comparison to the prior predictive distribution and our ERP
data. The prior and posterior predictions from the model with three cues show equally large effects of syntactic and semantic interference and an interaction. In contrast, the model using two cues, including a syntactic cue that utilizes syntactic hierarchy, predicts no effect of syntactic interference and no interaction, but a semantic interference effect. The model using one cue predicts no interference effects. The prior and posterior predictions of all models overlap with the effects of interest in the data. }

@@

\textcolor{blue}{To evaluate whether our new 2-cues model quantitatively outperforms the two other models in its predictive fit, we computed Bayes factors for the relevant model pairs under six different priors for the $F$ parameter 
($Normal$(0.01,0.01), 
$Normal$(0.01,0.02),
$Normal$(0.01,0.005),
$Normal$(0.02,0.01),
$Normal$(0.02,0.02),
$Normal$(0.02,0.005)). First, we computed the likelihood of the sampled $F$ parameters under each of the priors (LKL$_{F-prior}$) and the sampling prior (LKL$_{F-model}$). Then, the likelihood of the predicted semantic interference effect from the model was computed given the size of the observed semantic interference effect (LKL$_{predicted-effect}$). To obtain the marginal likelihood of the model, the product of LKL$_{predicted-effect}$ and LKL$_{F-prior}$ was divided by LKL$_{F-model}$. The marginal likelihood of the 2-cues model was then divided by the marginal likelihood of the three-cues and one-cue model, respectively. The resulting Bayes factors are shown in Figure \ref{fig:BF_compmods}. Compared to the null model with one cue, the Bayes factors provide extreme evidence for the new two-cues model. Therefore, we can conclude that the computational modeling shows that our data shows interference. Compared to the three-cues model proposed by \textcite{mertzen}, the Bayes factors provide moderate evidence for the new two-cues model. Therefore, the assumption that the relevant syntactic cue is the \{$\pm$subject-in-same-clause\} cue – rather than the previously assumed \{$\pm$grammatical subject\} cue – is moderately supported by these modeling results.
}

\begin{figure}
    \centering
    \caption{Comparison of the predictive accuracies of the three versions of the Lewis and Vasishth (2005) cue-based retrieval model on our ERP data. The facets show how the new two-cues model performs compared the the three-cues model and the one-cue model, respectively. Larger Bayes factors correspond to better performance of the two-cues model.}
    \label{fig:BF_compmods}
    \includegraphics[width=\linewidth]{images/BF_plot_compmodels.png}
\end{figure}

Thus, the theoretical assumption that is consistent with the observed ERP data is that although the parser uses the animacy cue exactly as proposed in previous work on cue-based retrieval, the syntactic cue keeps track of the clausal location of the subject. This is of course a speculative claim that would need to be further investigated empirically.

}%end copy
